---
title: "Improving r2dii.match"
description: |
  How to work with big data, and benchmarks of a more efficient version of `match_name()`
author:
  - name: Mauro Lepore
    url: https://github.com/maurolepore
date: 07-18-2020
output: 
  distill::distill_article:
  toc: true
  toc_depth: 3
  self_contained: true
categories:
  - r2dii
  - package
preview: preview.jpg
twitter:
  site: "@mauro_lepore"
  creator: "@mauro_lepore"
---

[`match_name()`](https://2degreesinvesting.github.io/r2dii.match/reference/match_name.html) may [run out of memory if your data is too big](https://github.com/2DegreesInvesting/r2dii.match/issues/214). Most software for data analysis has a limit to how much data it can handle with a given hardware. If your data is too big to run `match_name()` on your computer, consider using only a representative subset of data or a more powerful computer: For example, you may feed `match_name()` with data of only one sector (see [`filter()`](https://dplyr.tidyverse.org/reference/filter.html)), or with a small sample taken at random from all sectors (see [`slice_sample()`](https://dplyr.tidyverse.org/reference/slice.html));
alternatively, you may use the full dataset but run `match_name()` on a powerful [computer on the cloud](https://en.wikipedia.org/wiki/Cloud_computing#:~:text=Cloud%20computing%20is%20the%20on,many%20users%20over%20the%20Internet.). For more details, watch RStudio's webinar on [Working with Big Data in R](https://rstudio.com/resources/webinars/working-with-big-data-in-r/). 

However you use `match_name()`, it should use as little time and memory as it is reasonably possible. That is our goal. Here I compare two versions of `match_name()`: the version in development versus the version on CRAN (r2dii.match 0.0.3). Compared to the version on CRAN, the version in development uses a small fraction of the time and memory. The rest of this post shows the benchmarks.

***

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  comment = "#>",
  collapse = TRUE,
  # Benchmark each run
  cache = FALSE
)
```

Packages:

```{r message=FALSE, warning=FALSE}
library(bench)
library(devtools)
library(dplyr)
library(fs)
library(r2dii.data)
```

I'll use the names _devel_ and _cran_ to refer to the versions of `match_name()` that are, respectively, _in development_ and _on CRAN_ (r2dii.match 0.0.3).

```{r}
# The older version on CRAN
packageVersion("r2dii.match")
# Copy of match_name on CRAN
cran <- r2dii.match::match_name

# The newer version in development
suppressMessages(devtools::load_all(fs::path_home("git", "r2dii.match")))
packageVersion("r2dii.match")
# Copy of match_name in development
devel <- r2dii.match::match_name
```

Both versions have different source code:

```{r}
# Confirm the two versions of `match_name` are different
identical(devel, cran)
```

The version in development uses less memory and runs faster:

```{r}
benchmark <- bench::mark(
  # Don't check that the output is identical; rows-order is different^[1]
  check = FALSE,
  iterations = 5,
  matched_devel = matched_devel <- devel(loanbook_demo, ald_demo),
  matched_cran = matched_cran <- cran(loanbook_demo, ald_demo)
)

benchmark

benchmark %>%
  summarise(
    # How many times less memory uses the version in development?^[2]
    times_less_memory = as.double(mem_alloc)[[2]] / as.double(mem_alloc)[[1]],
    # How many times faster is the version in development?
    times_less_time = as.double(median)[[2]] / as.double(median)[[1]]
  )
```

* `[1]`: If we reorder the rows in the same way, both outputs are equivalent.

```{r}
# No output means that the two expressions are indeed equivalent
testthat::expect_equivalent(
  matched_devel %>% arrange(across(names(.))),
  matched_cran %>% arrange(across(names(.)))
)
```

* `[2]`: In RMarkdown I fail to get a result for `times_less_memory`. But in the console I get `times_less_memory` around 5.5.

Thanks to your feedback, `match_name()` is becoming more efficient. We expect to release the improved version on CRAN soon.
