---
title: "r2dii.data 0.1.0 is now on CRAN"
description: |
  This release includes new and improved datasets.
author:
  - name: Mauro Lepore
    url: https://github.com/maurolepore
base_url: https://2degreesinvesting.github.io/ds-at-2dii/
date: 2020-06-03
output: 
  distill::distill_article:
    toc: true
    toc_depth: 3
    self_contained: true
categories:
  - r2dii
  - software development
  - release
preview: preview.jpg
twitter:
  site: "@mauro_lepore"
  creator: "@mauro_lepore"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  collapse = TRUE,
  comment = "#>"
)
```

r2dii.data 0.1.0 is now on CRAN. r2dii.data provides public datasets to help you study how financial assets align to climate scenarios.

This release signals that r2dii.data is now [maturing](https://www.tidyverse.org/lifecycle/#maturing). You can install it from CRAN with:

```r
install.packages("r2dii.data")
```

Then use it with:

```{r}
library(r2dii.data)
```

I also use the package dplyr; it is not necessary but convenient.

```{r}
library(dplyr)
```

All user-facing changes are listed in the [changelog](https://2degreesinvesting.github.io/r2dii.data/news/index.html); here I'll show the most important ones.

We fixed a bug in the dataset `naics_classification`; it now contains the correct data.

```{r}
naics_classification
```

The dataset `region_isos` now includes the value "global" in the column `region`; it also gained the column `source`.

```{r}
region_isos %>% filter(region == "global")
```

The dataset `ald_demo` gained the column `ald_emission_factor_unit`.

```{r}
select(ald_demo, ald_emission_factor_unit)
```

Finally, we added three new datasets: `co2_intensity_scenario_demo`, `region_isos_demo`, and `scenario_demo_2020`.

```{r}
glimpse(region_isos_demo)

glimpse(scenario_demo_2020)

glimpse(co2_intensity_scenario_demo)
```

## Acknowledgements

```{r echo=FALSE}
thank <- function(x) {
  x <- sort(x)
  paste0("[", x, "]", sprintf("(https://github.com/%s)", x), collapse = ", ")
}
contributors <- c(
  "jdhoffa",
  "maurolepore"
)
```

While this release includes commits from only a few of us (`r thank(contributors)`), it is thanks to ideas and feedback from many more colleagues at 2DII.