---
title: "r2dii.analysis 0.0.1 is now on CRAN"
description: |
  Tools to calculate climate targets for financial portfolios
author:
  - name: Mauro Lepore
    url: https://github.com/maurolepore
base_url: https://2degreesinvesting.github.io/
date: 2020-06-29
output: 
  distill::distill_article:
    toc: true
    toc_depth: 3
    self_contained: true
categories:
  - r2dii
  - package
preview: preview.jpg
twitter:
  site: "@mauro_lepore"
  creator: "@mauro_lepore"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  collapse = TRUE,
  comment = "#>"
)
```

r2dii.analysis is an R package that provides tools to calculate climate targets for financial portfolios. The version 0.0.1 is the first one released on CRAN.

You can install it from CRAN with:

```r
install.packages("r2dii.analysis")
```

Then use it with:

```{r}
library(r2dii.analysis)
```

The best place to know about this package is on its [website](https://2degreesinvesting.github.io/r2dii.analysis/). The [home](https://2degreesinvesting.github.io/r2dii.analysis/index.html) page details how to install and use this package, and includes a number of useful links -- to try r2dii.analysis before you install it, to minimize installation errors, and to report bugs or raise issues. The navigation bar includes three important sections: (1) [_Get started_](https://2degreesinvesting.github.io/r2dii.analysis/articles/r2dii-analysis.html) introduces you to the package; (2) [_Reference_](https://2degreesinvesting.github.io/r2dii.analysis/reference/index.html) lists every feature and links to its help file; and (3) _Articles_ explains the [Sectoral Decarbonization Approach (SDA)](https://2degreesinvesting.github.io/r2dii.analysis/articles/target-sda.html), and the [Market Share Approach](https://2degreesinvesting.github.io/r2dii.analysis/articles/target-market-share.html).

As a preview, this snippet shows one feature of r2dii.analysis:

* Before you can use r2dii.analysis you need to load and prepare your data. Here I use toy data from the package r2dii.data, and two functions from the package r2dii.match.

```{r}
library(r2dii.match)
library(r2dii.data)

# Using the package r2dii.data to imitate loading data
loanbook <- loanbook_demo
ald <- ald_demo
co2 <- co2_intensity_scenario_demo

# Using the package r2dii.match to prepare the data
matched <- match_name(loanbook, ald) %>% prioritize()
```

* You can now use r2dii.analysis, for example, to calculate targets of CO2 emissions per unit production at the portfolio-level -- using the sectoral-decarbonization approach (SDA).

```{r}
matched %>% target_sda(ald = ald, co2_intensity_scenario = co2)
```

## Acknowledgements

```{r Acknowledgements, echo=FALSE}
thank <- function(x) {
  x <- sort(x)
  paste0("[", x, "]", sprintf("(https://github.com/%s)", x), collapse = ", ")
}
contributors <- c(
  "jdhoffa",
  "maurolepore",
  "Clare2D",
  "vintented"
)
```

Although this release includes commits from only a few contributors (`r thank(contributors)`), it is thanks to ideas and feedback from many more colleagues at 2DII.
