---
title: "r2dii suite is now on CRAN"
description: |
  R packages to implement the core functionality of the Paris Agreement Capital Transition Assessment (PACTA)
author:
  - name: Jackson Hoffart
    url: https://github.com/jdhoffa
date: "2020-06-30"
output: 
  distill::distill_article:
  toc: true
  toc_depth: 3
  self_contained: true
categories:
  - r2dii
  - package
preview: preview.jpg
twitter:
  site: "@jdhoffart"
  creator: "@jdhoffart"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  collapse = TRUE,
  comment = "#>"
)
```

_Adapted from <https://jdhoffa.github.io/blog/r2dii-suite-is-now-on-cran/>._

---

The core suite of r2dii packages ([r2dii.data](https://2degreesinvesting.github.io/r2dii.data/), [r2dii.match](https://2degreesinvesting.github.io/r2dii.match/) and [r2dii.analysis](https://2degreesinvesting.github.io/r2dii.analysis/)), are now published on CRAN!

The r2dii suite was developed to implement the core functionality of the [Paris Agreement Capital Transition Assessment (PACTA)](https://www.transitionmonitor.com/) in R. PACTA is a methodology which allows financial institutions to aggregate climate-related data associated to their portfolios, and compare the result against climate scenarios.

## Installation

You can easily install all three packages directly from CRAN using:

```r
r2dii <- c("r2dii.data", "r2dii.match", "r2dii.analysis")
install.packages(r2dii)
```

To get the latest development version any one package, you can install it from GitHub. Fir example, you can install r2dii.data from GitHub using:

```r
devtools::install_github("2DegreesInvesting/r2dii.data")
```

**Warning: Development versions are experimental and may be unstable. Proceed with caution.**

You can then use each package with `library()`.

```{r}
library(r2dii.data)
library(r2dii.match)
library(r2dii.analysis)
```

This example also uses two optional but convenient packages to manipulate and plot data:

```{r}
library(dplyr)
library(ggplot2)
```

## r2dii.data

[r2dii.data](https://2degreesinvesting.github.io/r2dii.data/) provides a series of fake datasets. These are mainly meant to be used as a tool to learn how the methodology works, and also to provide an easy sandbox for testing. The built-in `data_dictionary` provides a view of all datasets in the package, along with variable definitions:

```{r}
data_dictionary %>%
  distinct(dataset)
```

Some of the most useful datasets are:

* `loanbook_demo`: a loanbook dataset which can be used as a template to format real loanbook/ portfolio data. 
* `ald_demo`: a so-called "asset-level" dataset, containing crucial climate data at the asset level. (eg. power-plant capacity data, automotive car production, steel company emission factors)
* `scenario_demo_2020`: a fake climate scenario, offering technology pathways that would likely limit warming to less than 2 degrees Celsius. 

## r2dii.match

[r2dii.match](https://2degreesinvesting.github.io/r2dii.match/) provides the tools necessary to match the counter-parties in a loanbook to the climate data of the assets that they own. 

Owing to the fact that many lending portfolios are exposed to mid- and small- size companies, which are often not publicly-listed, matching data can be tricky. To achieve these links, we have written wrappers around some common fuzzy matching algorithms, which play nicely with formatted `loanbook`'s and `ald`'s. 

You can run the matching algorithm on sample data provided by `r2dii.data`:

```{r}
matched <- match_name(loanbook_demo, ald_demo)

matched %>%
  select(name, sector, name_ald, sector_ald, score)
```

After the initial matching, you must manually verify which of the matches you would like to keep. To do so, simply save `matched` as a .csv, and open in excel or similar. If you would like to keep a match, write the `score` to `1`. If you don't want the match, leave the `score` as anything but `1`:

```{r}
matched %>%
  filter(score != 1) %>%
  arrange(desc(score)) %>%
  select(name, sector, name_ald, sector_ald, score)
```

The final step is to prioritize your matches. This ensures that the same loan isn't accidentally matched to multiple `ald` companies. 

Read the validated match file back into R and run: 

```{r}
match_result <- matched %>%
  prioritize()

match_result %>%
  select(name_direct_loantaker, loan_size_outstanding, sector, name_ald)
```

## r2dii.analysis

The final step is to analyze your matched dataset, and compare the results to a climate scenario. 

You can apply scenario targets to your loanbook data by calling: 

```{r}
portfolio_targets <- match_result %>%
  target_market_share(
    ald_demo,
    scenario_demo_2020,
    region_isos_demo
  )

portfolio_targets
```

And you can plot the distribution of technologies using `ggplot2`:

```{r}
portfolio_targets %>%
  # different targets can be plotted by setting these filters
  filter(
    sector == "power",
    weighted_production_metric != "normalized_corporate_economy",
    year == max(year)
  ) %>%
  group_by(technology) %>%
  ggplot(aes(
    x = weighted_production_metric, 
    y = weighted_production_value, 
    fill = technology
  )) +
  geom_col(position = "fill") +
  labs(
    x = "Metric",
    y = "Weighted Capacity [%]"
  )
```
